### 2019-01-17 Sections/economics_of_the_quantum_internet.tex
Economics++

\subsection{Cooperative payoff enhancement}\index{Cooperative payoff enhancement}

@@

	\[\mathrm{Model}\] & \[\mathrm{General\, form}\] & \[f_\mathrm{sc}(n)=n\] & \[f_\mathrm{sc}(n)=n^p\] & \[f_\mathrm{sc}(n)=e^n\]\\

@@

@@

\captionspacetab \caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\mathrm{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\mathrm{global}=\sum_{j\in \mathrm{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\mathrm{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\mathrm{rf}$ is the risk-free rate of return (typically yield on US government bonds). $\gamma_T$ is the rate of taxation, and $N_\mathrm{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}

>>>>

\subsection{Cooperative payoff enhancement}\index{Cooperative payoff enhancement}\label{sec:coop_enh}

@@

	\[\mathrm{Model}\] & \[\mathrm{General\, form}\] & \[f_\mathrm{sc}(n)=n\] \begin{center}(classical)\end{center} & \[f_\mathrm{sc}(n)=n^p\] \begin{center}(intermediate)\end{center} & \[f_\mathrm{sc}(n)=e^n\] \begin{center}(full quantum)\end{center}\\

@@

	\begin{flushleft}Cooperative payoff enhancement (Sec.~\ref{sec:coop_enh})\end{flushleft} & \[c_X = \frac{n_X\cdot f^X_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y} \] & \[ n_X\] & \[ n_X(n_X+n_Y)^{p-1} \] & \[ \frac{n_X\cdot e^{n_X+n_Y}}{n_X+n_Y}\] \\

@@

\captionspacetab \caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\mathrm{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\mathrm{global}=\sum_{j\in \mathrm{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\mathrm{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\mathrm{rf}$ is the risk-free rate of return (typically the yield on US government bonds). $\gamma_T$ is the rate of taxation, and $N_\mathrm{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}
